\documentclass{article}
\usepackage[utf8]{inputenc}

\title{PS1}
\author{myuhas5120 }
\date{January 19th 2018}


\begin{document}

\maketitle

\section{Why Econ and Data Science}
Economics is all about quantifying human behavior in an attempt to better understand human interaction and valuation. As we are better able to gather data concerning all forms of human interaction, the next logical step is discovering how to parse through the data in search of significant trends that will better allow us to predict human interaction.  Data science is that next step.

For my project, I had thought about working with voting data to look at gerrymandering and attempting to determine which states were the most egregious participants.  Alternatively, I am also curious in looking at trends in the increase of craft breweries across the western half of the United States and how that interacts with profits and consumption.

Over the duration of this class, I plan on becoming more fluent in R as well as becoming familiar with the use of Julia and Python.   I also want to learn how to improve my coding practices for better discipline and comprehensibility.  Additionally, I want to learn how to create more accurate statistical models that surpass the simple regression models that I have learned up to this point.  Finally,  I want to learn the basics of machine learning, as automation is always preferable to brute handiwork.

Post graduation, I would like to find a position in a consulting firm as an economic analyst.  In an idealized scenario, that position will involve international travel with short to mid-term postings(3 weeks to a year).  Regardless, I hope to be involved in consulting on problems concerning logistics and resource management. 

\section{Equation}
\[a^2 + b^2 = c^2 \]

\end{document}
